%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% ---------------------------------------------------------
\cvmultientry
{Johnson Controls} % Organization
{}
{Oct. 2011 - Jan. 2020} % Dates
{
% \begin{cvsubentries}
\cvsubentry
{Principal Research Engineer} % Job title
{Milwaukee, WI} % Location
{Dec. 2017 - Jan. 2018} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I used advanced optimization and data analytics methods to improve the efficiency of heating, ventilation and air conditioning (HVAC) systems.}
\item {I was involved in the transfer of newly developed technology into products and applications.}
\end{cvitems}
}
\cvsubentry
{Senior Research Engineer} % Job title
{Milwaukee, WI} % Location
{May 2015 - Dec. 2017} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed methods for monitoring the performance of PID controllers, to detect steady state operation of HVAC equipment, and reduce energy consumption in wireless thermostats while keeping acceptable comfort standards. I used advanced mathematical tools to develop these methods, as well as artificial intelligence, machine learning and traditional statistical methods.}
\end{cvitems}
}
\cvsubentry
{Senior Research Engineer} % Job title
{Mexico City, Mexico} % Location
{Jan. 2013 - May 2015} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed data-driven methods for fault detection and diagnosis in connected chillers.}
\end{cvitems}
}
%---------------------------------------------------------
\cvsubentry
{Senior Research Engineer} % Job title
{Milwaukee, WI} % Location
{Oct. 2011 - Jan. 2013} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed a method for adaptive sampling of PID controllers.}
\end{cvitems}
}
% \end{cvsubentries}
}
%---------------------------------------------------------
\vspace{1mm}
\cventry
{The Dow Chemical Company} % Organization
{Freeport, TX} % Location
{May 2010 - Aug. 2010} % Date(s)
{Summer Research Intern} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed an Excel application for multivariate statistical monitoring of continuous and batch processes.}
\end{cvitems}
}
%---------------------------------------------------------
\cvmultientry
{Capstone Technology} % Organization
{Seattle, WA}
{2006 - 2009} % Date(s)
{
% \begin{cvsubentries}
\cvsubentry
{Summer Engineering Intern} % Job title
{} % Location
{May. 2009 - Aug. 2009} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed a multivariate image analysis application to monitor combustion efficiency in furnaces.}
\end{cvitems}
}
\cvsubentry
{Summer Engineering Intern} % Job title
{} % Location
{May. 2007 - Aug. 2007} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed a multivariate statistical application for statistical modeling and prediction in chemical processes.}
\end{cvitems}
}
\cvsubentry
{Summer Engineering Intern} % Job title
{} % Location
{May. 2006 - Aug. 2006} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed a multivariate statistical application for detection and diagnosis of sensor and process faults.}
\end{cvitems}
}
% \end{cvsubentries}
}

\cventry
{NMC North Microelectronics} % Organization
{Beijing, China} % Location
{Jun. 2008 - Jul. 2008} % Date(s)
{Summer Engineering Intern} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {I developed a multivariate statistical application for monitoring the operation of a semiconductor manufacturing process.}
\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
