%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Internship Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
{The Dow Chemical Company} % Organization
{Freeport, TX} % Location
{May 2010 - Aug. 2010} % Date(s)
{Summer Research Intern} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed a VBA application for multivariate statistical monitoring of continuous and batch processes.}
\end{cvitems}
}%
%---------------------------------------------------------
\cvmultientry
{Capstone Technology} % Organization
{Seattle, WA}
{2006 - 2009} % Date(s)
{
% \begin{cvsubentries}
\cvsubentry
{Summer Engineering Intern} % Job title
{} % Location
{May. 2009 - Aug. 2009} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed a multivariate image analysis application to monitor combustion efficiency in furnaces.}
\end{cvitems}
}%
\cvsubentry
{Summer Engineering Intern} % Job title
{} % Location
{May. 2007 - Aug. 2007} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed a multivariate statistical application for statistical modeling and prediction in chemical processes.}
\end{cvitems}
}%
\cvsubentry
{Summer Engineering Intern} % Job title
{} % Location
{May. 2006 - Aug. 2006} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed a multivariate statistical application for detection and diagnosis of sensor and process faults.}
\end{cvitems}
}
% \end{cvsubentries}
}

\cventry
{NMC North Microelectronics} % Organization
{Beijing, China} % Location
{Jun. 2008 - Jul. 2008} % Date(s)
{Summer Engineering Intern} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed a multivariate statistical application for monitoring the operation of a semiconductor manufacturing process.}
\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
