%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{fancy}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{banking}             % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{marvosym}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% \usepackage{color,hyperref}
% \definecolor{darkblue}{rgb}{0.0,0.0,0.3}
% \hypersetup{colorlinks,breaklinks,
%             linkcolor=darkblue,urlcolor=darkblue,
%             anchorcolor=darkblue,citecolor=darkblue}

%Change the font to Myriad
\renewcommand{\sfdefault}{Myriad-LF}
% \usepackage[protrusion=true,expansion=true]{microtype}

% personal data
\firstname{Carlos Felipe}
\familyname{Alcal\'a P\'erez}
%\title{}               % optional, remove the line if not wanted
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
\address{507 E Michigan St, M36, Milwaukee}{Wisconsin, 53202. USA.}    % optional, remove the line if not wanted
\mobile{+1 414 426 6814}                    % optional, remove the line if not wanted
\phone{+1 414 524 5886}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{Carlos.Alcala@jci.com}                     % optional, remove the line if not wanted
%\photo[85pt]{Carlos3.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
    \cventry{August 2011}{Doctor of Philosophy in Chemical Engineering}{\href{http://chems.usc.edu/faculty_staff/scholars/calcala.htm}{University of Southern California}}{}{}{Los Angeles, California.}

    \cventry{May 2007}{Master of Science in Chemical Engineering}{\href{http://www.che.utexas.edu/}{The University of Texas at Austin}}{}{}{Austin, Texas.}

    \cventry{May 2004}{Bachelor of Science in Chemical Engineering}{\href{http://www.itcm.edu.mx/}{Technological Institute of Ciudad Madero}}{}{}{Summa Cum Laude. Ciudad Madero, Mexico.}
%    \cvline{}{GPA: 3.920}

\section{Research Interests}
    \cvline{}{Multivariate Statistical Fault Detection and Diagnosis, Data Analysis, Machine Learning, Tuning and Monitoring of PID Controllers}

\section{Experience}


    \cventry{Present \quad October 2011}{Senior Research Engineer}{\href{http://www.johnsoncontrols.com}{Johnson Controls, Inc}}{}{}{507 E Michigan Street, M61. Milwaukee, Wisconsin, 53202. USA.}
    \cvline{}{\small Development of methods for fault detection and diagnosis in connected chillers.}
    \cvline{}{\small Development of methods for adaptive sampling of PID controllers.}
    \cvline{}{\small Development of methods for monitoring the performance of PID controllers.}

    % \cventry{December 2012 October 2011}{Senior Research Engineer}{\href{http://www.johnsoncontrols.com}{Johnson Controls, Inc}}{}{}{507 E Michigan Street, M61. Milwaukee, Wisconsin, 53202. USA.}
    % \cvline{}{\small Development of strategies for adaptive tuning of PID controllers.}
    % \cvline{}{\small Development of methods for fault detection and diagnosis in thermal systems.}
    % \cvline{}{\small Development of strategies for large scale simulation of thermal systems.}

    \cventry{Summer 2010}{Research Intern}{\href{http://www.dow.com/}{The Dow Chemical Company}}{}{}{2301 North Brazosport Boulevard, Freeport, Texas 77541, USA.}
    \cvline{}{\small Developed an Excel application for multivariate statistical monitoring of continuous and batch processes.}

    \cventry{Summer 2009 Summer 2007 Summer 2006}{Engineering Intern}{\href{http://www.capstonetechnology.com/soft-sensors.aspx}{Capstone Technology}}{}{}{8350 28th Ave NW Seattle, Washington 98117. USA.}
    \cvline{}{\small Developed a PLS application for statistical modeling of chemical processes.}
    \cvline{}{\small Developed a multivariate image analysis application to monitor combustion efficiency in furnaces.}
    \cvline{}{\small Developed a PCA application for detection and diagnosis of sensor and process faults.}


    \cventry{Summer 2008}{Engineering Intern}{NMC North Microelectronics}{}{}{No.1 East Jiuxianqiao Rd., Chaoyang Dist., Beijing 100016, China}
    \cvline{}{\small Developed a PCA application for monitoring the operation of a semiconductor manufacturing process.}

% \vspace{2cm}

\section{Academic Honors}
    \cvline{USC, 2007, 2010} {\href{http://www.robertorocca.org/en/fellowships/fellows07.aspx}{Roberto Rocca Education Program Fellowship}}
    \cvline{Texas, 2005}{\href{http://fulbright.state.gov/}{Fulbright Scholarship}}

%    \cvline{Texas, 2006}{\href{http://www.utexas.edu/ogs/funding/fellowships/continuing/}{David Bruton, Jr. Fellowship}}
%    \cvline{Texas, 2005}{\href{http://www.engr.utexas.edu/undergraduate/scholarships}{College of Engineering Fellowship at UT Austin}}

%    \subsection{Undergraduate}
%    \cventry{Mexico, 2003}{1st National place}{Chemistry}{}{}{ 11th National Basic Sciences Contest of Technological Institutes.}
%
%    \cventry{Mexico, 2002}{1st National place}{Mathematics, Physics and Chemistry}{}{}{10th National Basic Sciences Contest of Technological Institutes.}



 %   \section{Languages}
 %       \cvlanguage{Native}{Spanish}{Fluent}
%        \cvlanguage{Second}{English}{Fluent}


    \section{Computer skills}
        \cvline{Languages}{R, Matlab, \LaTeX, Markdown, Python, C\#, Modelica, VB.NET, VBA}{}{}
        \cvline{Applications}{Sublime Text, RStudio, Matlab, Simulink, Dymola, MS Office }{}{}

    \section{Patents}
    \subsection{Granted}
    \cvline{}{Carlos Felipe Alcala Perez, Timothy I. Salsbury. ``Systems and methods for adaptive sampling rate adjustment''. Patent US 20140257528. September 11, 2014. Source: \href{http://www.google.com/patents/US20140257528} {US20140257528} }
    \subsection{Filed}
    \cvline{}{Carlos Felipe Alcala Perez. ``Building management system with voting-based fault detection and diagnosis.''. Filed on June 2015.}
    \cvline{}{Timothy I. Salsbury, Carlos F. Alcala. ``Normalized indices for feedback control loops.''. Filed on August 2014.}

    \section{Publications}
    \subsection{Journal Papers}
    \cvline{}{Carlos F. Alcala and S. Joe Qin. Reconstruction-Based Contribution for Process Monitoring. \textit{Automatica}, 2009 (45), 1596-1600. DOI: \href{http://dx.doi.org/10.1016/j.automatica.2009.02.027} {10.1016/j.automatica.2009.02.027}}

    \cvline{}{Carlos F. Alcala and S. Joe Qin. Reconstruction-Based Contribution for Process Monitoring with Kernel Principal Component Analysis. \textit{Industrial Engineering and Chemistry Research}. 2010 (49), 7849-7857. DOI: \href{http://pubs.acs.org/doi/abs/10.1021/ie9018947}{10.1021/ie9018947}.}

    \cvline{}{Gang Li, Carlos F. Alcala, S. Joe Qin and Donghua Zhou. Generalized Reconstruction-Based Contributions for Output-Relevant Fault Diagnosis With Application to the Tennessee Eastman Process. \textit{IEEE Transactions on Control Systems Technology}. 2010. DOI: \href{http://dx.doi.org/10.1109/TCST.2010.2071415}{10.1109/TCST.2010.2071415}.}
    \cvline{}{Carlos F. Alcala and S. Joe Qin. Analysis and Generalization of Fault Diagnosis Methods for Process Monitoring. \textit{Journal of Process Control}. 2011 (21), 322-330. DOI: \href{http://dx.doi.org/10.1016/j.jprocont.2010.10.005}{10.1016/j.jprocont.2010.10.005} }

    \subsection{Conference Papers}
    \cvline{}{Timothy I. Salsbury and Carlos F. Alcala. Two New Normalized EWMA-based Indices for Control Loop Performance Assessment. \textit{In Proceedings of the 2015 American Control Conference}, Chicago, Illinois, July 2015.}
    \cvline{}{Carlos F. Alcala and S. Joe Qin. Unified Analysis of Diagnosis Methods for Process Monitoring. \textit{In Proceedings of the $7^{th}$ IFAC SafeProcess Symposium}, Barcelona, Spain, July 2009.}
    \cvline{}{Carlos F. Alcala and S. Joe Qin. Unification of Contribution Analysis for Process Monitoring. \textit{In Proceedings of the AIChE Annual Meeting}, Philadelphia, November 2008.}
    \cvline{}{Carlos Alcala and S. Joe Qin. Reconstruction-Based Contribution for Process Monitoring, \textit{In Proceedings of the $17^{th}$ IFAC World Congress}, Seoul, Korea, July 2008.}

\end{document}



