%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Cover Letter
% XeLaTeX Template
% Version 1.0 (1/11/15)
%
% This template has been downloaded from:
% https://github.com/mlda065/friggeri-letter
%
% Original author:
% Matthew Davis, based on code by
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX
% You may need to compile twice for the header to appear.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,english]{friggeri-letter}
\usepackage[utf8]{inputenc}

\usepackage{babel}

\begin{document}

\header{Carlos Felipe~}{Alcala Perez}{Principal Research Engineer}

\address{
   1406 E Russell Ave \\
   Milwaukee, Wisconsin
}


\letter{
   Hiring Manager \\
   Company
}

\opening{Dear Hiring Manager:}

I am currently a researcher at Johnson Controls with 8 years of experience in the field of process control and building efficiency. Due to my educational background, and experience working at JCI, I have gathered a unique set of skills that fall in the Data Science domain, and I want to transition to that field.

I'm a very experienced user of R and several of its packages, and have experience with the Python programming language. I can automate the gathering, cleaning, modeling, analysis and visualization of large amounts of data. I am familiar with several statistics and machine learning techniques to build descriptive and predictive models, and, as a visual person, I can handle several tools to create visualizations and tell compelling stories with data.

I am a self-motivated person with great analytical and modeling skills due to my PhD in Chemical Engineering. I have also very good interpersonal skills that allow me to connect with people and collaborate with them effortlessly. Furthermore, I am a quick learner that can get up-to-speed quickly with new methods, tools and concepts.

I'm looking for new opportunities to apply my skills as a Data Scientist, and would be glad to hear about opportunities in your organization.


\closing{
   Yours Sincerely\\
   Carlos Alcala}

\end{document}
