%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{biblatex}
\addbibresource{../../bib/alcala-bibliography.bib} % Specify the bibliography file to include publications

\RequirePackage{marvosym}
\hypersetup{
	hidelinks=true
}

\begin{document}

\header{Carlos Felipe~}{Alcala Perez}{Principal Research Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
507 E. Michigan St
Milwaukee, Wisconsin 53202, USA
~
\Mobilefone~ +1 (414) 426 6814
% \Telefon~ +1 (414) 524 5886
~
% \href{mailto:alcala21@gmail.com}{alcala21@gmail.com}
\href{mailto:carlos.alcala@jci.com}{carlos.alcala@jci.com}
\href{https://www.linkedin.com/in/alcala21}{LinkedIn://alcala21}
\href{https://www.github.com/alcala21}{GitHub://alcala21}
% \href{http://facebook.com/johnsmith}{fb://jsmith}
\section{languages}
spanish (native)
english (fluent)
\section{programming}
R, Python, Matlab,
Modelica, \LaTeX, 
RMarkdown, Bash
\section{applications}
Simulink, Dymola,
RStudio, Git, Github,
Visual Studio Code
\section{certifications}
\href{https://www.coursera.org/account/accomplishments/specialization/certificate/UWG3PS5EXMBJ}{Statistics with R}
\href{https://www.coursera.org/account/accomplishments/specialization/certificate/2VHFDHW5GUK6}{Machine Learning}
\href{https://www.coursera.org/account/accomplishments/specialization/certificate/W9DB45S3CGDZ}{Data Science}
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2007--2011}
{Doctor of Philosophy {\normalfont in Chemical Engineering}}
{\flushright \href{http://chems.usc.edu}{University of Southern California.} Los Angeles, California.}
% {Dissertation about fault detection and diagnosis.}

%------------------------------------------------

\entry
{2005--2007}
{Master of Science {\normalfont in Chemical Engineering}}
{\flushright \href{http://www.che.utexas.edu/}{The University of Texas at Austin.}
Austin, Texas.}
% {\emph{Money Is The Root Of All Evil -- Or Is It?} \\ This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}

%------------------------------------------------

\entry
{1999--2004}
{Bachelor of Science {\normalfont in Chemical Engineering}}
{\flushright \href{http://www.itcm.edu.mx/}{Technological Institute of Ciudad Madero}.
Ciudad Madero, Mexico}
{Summa Cum Laude.}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------
\section{research interests}
Multivariate Statistical Fault Detection and Diagnosis, Data Analysis, Machine Learning, Tuning and Monitoring of PID Controllers, Optimization, Self-optimizing control, Extremum-seeking control
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{full time}

\begin{entrylist}

%------------------------------------------------

\entry
{2017 -- Now}
{\href{http://www.johnsoncontrols.com}{Johnson Controls International}}
{Milwaukee, Wisconsin.}
{
\emph{Principal Research Engineer.}
\begin{itemize}
	\item I am currently working in the development and implementation of self-optimizing control methods to improve the efficiency of heating, ventilation and air conditioning (HVAC) systems. A patent has been filed.
	\item I am working in the implementation of artificial intelligence methods to optimize the operation of HVAC systems. A patent has been filed.
	\item I am involved in the development and transfer of research projects into products and applications.
   \item I worked in the development of methods to reject pressure disturbances in control valves. A patent was filed.
   
\end{itemize}
}
\entry
{2015 -- 2017}
{\href{http://www.johnsoncontrols.com}{Johnson Controls International}}
{Milwaukee, Wisconsin.}
{
\emph{Senior Research Engineer}
\begin{itemize}
\item Developed methods for monitoring the performance of PID controllers. Three patents were granted.
\item Developed a method to detect steady state operation in HVAC equipment. A patent was filed.
\item Developed method to reduce energy consumption in wireless thermostats while keeping acceptable comfort standards. A patent was filed, and another one was granted.
\end{itemize}
}

\entry
{2013 -- 2015}
{\href{http://www.johnsoncontrols.com/es_mx}{Johnson Controls BE Servicios}}
{Mexico City, Mexico.}
{
\emph{Senior Research Engineer}
\begin{itemize}
\item Developed data-driven methods for fault detection and diagnosis in connected chillers. A patent was filed.
\end{itemize}
}

\entry
{2011 -- 2013}
{\href{http://www.johnsoncontrols.com}{Johnson Controls, Inc}}
{Milwaukee, Wisconsin.}
{
\emph{Senior Research Engineer}
\begin{itemize}
\item Developed a method for adaptive sampling of PID controllers. A patent was granted.
\end{itemize}
}
%------------------------------------------------

\end{entrylist}

% \pagebreak

\subsection{internships}

\begin{entrylist}

\entry
{2010}
{\href{http://www.dow.com/}{The Dow Chemical Company}}
{Freeport, Texas}
{\emph{Summer Research Intern} \\
Developed an Excel application for multivariate statistical monitoring of continuous and batch processes.}

%------------------------------------------------

\entry
{\begin{minipage}[t]{2cm}2009 \\ 2007 \\ 2006\end{minipage}}
{\href{http://www.capstonetechnology.com}{Capstone Technology}}
{Seattle, Washington}
{\emph{Summer Engineering Intern}
\begin{itemize}
	\item Developed a multivariate image analysis application to monitor combustion efficiency in furnaces.
	\item Developed a PLS application for statistical modeling of chemical processes.
	\item Developed a PCA application for detection and diagnosis of sensor and process faults.
\end{itemize}}

%------------------------------------------------

\entry
{2008}
{NMC North Microelectronics}
{Beijing, China}
{\emph{Summer Engineering Intern}
\begin{itemize}
	\item Developed a PCA application for monitoring the operation of a semiconductor manufacturing process.
\end{itemize}}

%------------------------------------------------




\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2015}
{1st Place - 2015 BE TechChallenge}
{Building Efficiency, Johnson Controls Inc.}
{I won the annual company-wide innovation competition at JCI.}

\entry
{2007}
{\href{http://www.robertorocca.org/en/fellowships/fellows07.aspx}{Roberto Rocca Fellowship}}
{University of Southern California}
{I was awarded a fellowship from the Roberto Rocca Education Program to do my PhD at USC.}

\entry
{2005}
{Fulbright Scholarship}
{University of Texas at Austin}
{I was awarded a Fulbright scholarship to do my Masters degree at UT Austin.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{interests}

% \textbf{professional:} data analysis, company profiling, risk analysis, economics, web design, web app creation, software design, marketing \textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{misc}{Patents} % Print all miscellaneous entries from the bibliography

\printbibsection{article}{Journal Papers} % Print all articles from the bibliography

\printbibsection{inproceedings}{Conference Papers} % Print all books from the bibliography

% \begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
% \nocite{*}
% \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
% \end{refsection}

% \begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
% \nocite{*}
% \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
% \end{refsection}



% \printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}